A Large-scale Study of Polymorphism in R

### 2019-03-28 notebooks/paper_results_section.Rmd
new data, and some top poly by size info

Get the biggest signature.
```{r}
big <- get_biggest_function(los, metric=size_of_signature_type)

# it's %>%
```

>>>>

Get the biggest signatures.
```{r}
lo_sizes <- get_X_biggest_functions(los, metric = size_of_signature_type)

top_10_big <- head(lo_sizes, 10)

# make df
top_10_big_df <- data.frame(
  pkg = sapply(names(top_10_big), function(n) strsplit(n, split="::")[[1]][1]),
  fun = sapply(names(top_10_big), function(n) strsplit(n, split="::")[[1]][2]),
  size = top_10_big
)

rownames(top_10_big_df) <- NULL

top_10_big_df %>% xtable

```

### 2019-03-28 paper/main.tex
new data, and some top poly by size info

\AT{I'll explain this better, maybe?}
In Figure~\ref{fig:dfdbl}, we see a function that, among other things, takes in some data ({\tt dat}) and a character string ({\tt spss}) specifying either {\tt "in"} or {\tt "out"}.
Now, depending on the value of {\tt spss}, {\tt dat} will either be a data frame or a vector of doubles.
\AT{This ties in to the (arg, retv) coupling, which we will have data on soon.}

@@

\AT{Meta-Comment:} My plan for this section is to linearly go through the
data, and show logical transitions between various type systems.  I'll start
with the finest-grained one.

@@

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
> add_make_list <- function(x, y) as.list(x + y)
> add_make_list(2, c(3, 1)) # => list(5, 3)
\end{lstlisting}}
\begin{tabular}{@{}r|l|l|l@{}}\hline
\bf Argument & \bf Type & \bf Class &\bf Attributes \\
x & \tt scalar/double & \tt numeric & \tt \{\} \\
y & \tt vector/double & \tt numeric & \tt \{\} \\
retv & \tt list<double> & \tt list & \tt \{\}  
\end{tabular}
\caption{Example call and FGTS signature}\label{fig:exFGTS}\end{figure}

@@

%
%
%
%
\AT{We might want to discuss some of the most polymorphic functions in the language.}
\subsection{Most Polymorphic Functions}

@@

Now, depending on the granularity of individual argument annotations, we might want to link certain arguments together.
Consider the code snippet in Figure~\ref{fig:indexof}
\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
access <- function(l, i) l[[i]]

>>>>

\AT{I'll explain this better, maybe?}
In Figure~\ref{fig:dfdbl}, we see a function that, among other things, takes in some data ({\tt dat}) and a character string ({\tt spss}) specifying either {\tt "in"} or {\tt "out"}.
Now, depending on the value of {\tt spss}, {\tt dat} will either be a data frame or a vector of doubles.

@@

\AT{Note:} My plan for this section is to linearly go through the
data, and show logical transitions between various type systems.  I'll start
with the finest-grained one.
\AT{End Note.}

@@

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
add_make_list <- function(x, y) {
  l <- as.list(x + y)
  attr(l, "example") <- "this is an attribute"
  l
}
add_make_list(2, c(3, 1)) # => list(5, 3)
\end{lstlisting}}
\begin{tabular}{@{}r|l|l|l@{}}\hline
\bf Argument & \bf Type & \bf Class &\bf Attributes \\
x & \tt scalar/double & \tt numeric & \tt \{\} \\
y & \tt vector/double & \tt numeric & \tt \{\} \\
retv & \tt list<double> & \tt list & \tt \{example: scalar/character\}  
\end{tabular}
\caption{Example call and FGTS signature}\label{fig:exFGTS}\end{figure}

@@

%
%
%
%
\AT{We might want to discuss some of the most polymorphic functions in the language.}
\subsection{R's Most Polymorphic Functions}

In this section, our goal is to shed some light on the most polymorphic functions in R.
Table~\ref{tab:bigpolyfuns} shows the 10 functions with the biggest recorded signatures.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 28 16:01:37 2019
\begin{table}[ht]
\label{tab:bigpolyfuns}
\centering
\begin{tabular}{llrl}
  \hline
Package & Function & Size & Description \\ 
  \hline
magrittr & \%$>$\% & 23.00 & Tidyverse pipe function \\ 
  magrittr & freduce & 17.67 & Apply a list of functions sequentially \\ 
  rlang & captureArgInfo & 16.50 & Capture arg info \\ 
  rlang & enquo & 16.00 & Create quosure \\ 
  rlang & get\_expr & 15.00 & Extract expression \\ 
  data.table & replace\_dot\_alias & 13.50 & Deals with '.' in passed expr \\ 
  tibble & strip\_dim & 13.00 & Removes 'dim' attribute \\ 
  data.table & copy & 11.00 & Create copy of passed value \\ 
  htmlwidgets & shouldEval & 11.00 & Eval passed value depending on tag \\ 
  magrittr & \%$<$$>$\% & 11.00 & Like \%$>$\% but assigns \\ 
   \hline
\end{tabular}
\caption{10 most polymorphic functions.}
\end{table}

The size metric we use is roughly the size of each individual argument signature, divided by the number of function arguments.
The division is performed to avoid unfairly favouring functions with many arguments.

@@

Now, depending on the granularity of individual argument annotations, we might want to link certain arguments together.
Consider the code snippet in Figure~\ref{fig:indexof}.
\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
access <- function(l, i) l[[i]]
